---
title: "hw_09"
author: "Trystan A. Bordeau"
date: "11/3/2020"
output: github_document
---

# Homework #9: Functions and Programming 

Write a function to calculate the variance of a numeric vector. Before we begin, we must load in tidyverse and other needed packages

```{r}
library(tidyverse)
library(ggplot2)
```
# 1. Variance
Next, lets create a vector with different variables and create a code that finds variance (V)
```{r}
set.seed(1)
a1 <- sample(1:20, 10)
a1
```

Now that we have data lets create the function 
```{r}
Variance <- function(x) {
x <- as.numeric(as.character(x))[!is.na(as.numeric(as.character(x)))]
sum((x-mean(x))^2) / (length(x)-1)
}

Variance(a1)
```

# 2. Write both_na(), a function that takes two vectors of the same length and returns the number of positions that have an NA in both vectors

```{r}
both_na <- function(x, y) {
  sum(is.na(x) & is.na(y))
}
both_na(
  c(NA, 4, 1, NA), 
  c(NA, 1, NA, NA)
)

# shows there are two NA's in the same position
```

# 3. Write a function to create a specific kind of plot that can take a data frame as an argument

```{r}
plot <- function(mtcars){
  ggplot(aes(x = cyl, y = mpg)) +
    geom_point() + 
labs(x = "Cylinders", y = "Miles per Gallon")
  plot
}

```
# 4. 

# 5. 

# 6. 

```{r}
system.time(for (i in 1:1000000) 
  (i + i))
#This took roughly .022 seconds to perfomr this calculation
```
```{r}

```

