---
title: "hw_08"
author: "Trystan A. Bordeau"
date: "10/17/2020"
output: github_document
---

# Homework 8: More Data Wrangling 


#Lists, data frames, and vectors

We must first call in the packages that we will be using

```{r}
library(tidyverse)
library(nycflights13)
```

Next, lets create a list (using the list() function) to call three named elements. I will be using mtcars, diamonds, and letters as my three elements 

```{r}
my_list <- list(data_frame_1 = mtcars, 
                data_frame_2 = diamonds, 
                data_frame_3 = letters)
```

Now lets access the first element by name using $

```{r}
my_list$data_frame_1
```

Now lets access the second element using [[ ]] function 

```{r}
my_list[["data_frame_2"]]
```

Now lets access the third element as a list using the [ ] syntax 

```{r}
my_list["data_frame_3"]
```

Using mtcars, access the mpg column in two different ways 

```{r}
mtcars["mpg"]
```

```{r}
mtcars %>%
  select(mpg)
```

Now, we will create a new column in mtcars that displays displacement per cylinder (engine displacment divided by cylinders)

```{r}
mtcars["displacement.per.cylinder"] <- mtcars$disp / mtcars$cyl
```

Now we will create a single column data frame using the mutate() function

```{r}
mtcars <- mtcars
disp_cyl <- mtcars %>%
  mutate(disp_cyl = (paste(disp/cyl))) %>%
  select(disp_cyl)
```


# Factors 

Create a numeric vector (I will use the one given to us in the assignment)

```{r}
num.vec <- c(3, 4, 1, 5)
```

use as.factor() to convert the numeric vector to a factor 

```{r}
factor <- as.factor(num.vec)
```

use as.numeric() to convert that factor to a numeric vector 

```{r}
as.numeric(factor)
```


# Exploratory Data Analysis

Now, lets use the babynames dataset to do some exploratory data analysis. 

First, we must install the babynames package 

```{r}
library(nycflights13)
library("tidyverse")
library(dplyr)
```

Now, lets write some code and explore the data that we have here! 

```{r}
?nycflights13::flights
ggplot(data = flights, aes(x = flight, y = tailnum)) 
```

